Hydras \& Co.

### 2022-02-15 doc/gaia-chapter.tex
small module restructuration

\begin{itemize}
\item In
  \href{../theories/html/gaia_hydras.T1Bridge_use.html}%
  {\texttt{gaia\_hydras.T1Bridge\_use}}, we adopt \HydrasLib's point of view, and the name \texttt{T1} is by default bound to
\HydrasLib' data structures.

\inputsnippets{T1Bridge_use/T1BridgeUse,
  T1Bridge_use/LocateT1}

@@

\inputsnippets{T1Bridge_use/T1BridgeUseb}

@@

The module~\href{../theories/html/gaia_hydras.T1Bridge_use.html}%
{\texttt{gaia\_hydras.T1Bridge\_use}} shows a small
example of importation of \texttt{multA} into \texttt{hydra-battles}' world.

\inputsnippets{T1Bridge_use/T1BridgeUse}

@@

 \inputsnippets{ T1Bridge_use/LocateT1, T1Bridge_use/T1BridgeUseb}

>>>>

\begin{itemize}
\item In
  \href{../theories/html/gaia_hydras.GaiaToHydra.html}%
  {\texttt{gaia\_hydras.GaiaToHydra}}, we adopt \HydrasLib's point of view, and the name \texttt{T1} is by default bound to
\HydrasLib' data structures.

\inputsnippets{GaiaToHydra/T1BridgeUse,
  GaiaToHydra/LocateT1}

@@

\inputsnippets{GaiaToHydra/T1BridgeUseb}

@@

The module~\href{../theories/html/gaia_hydras.GaiaToHydra.html}%
{\texttt{gaia\_hydras.GaiaToHydra}} shows a small
example of importation of \texttt{multA} into \texttt{hydra-battles}' world.

\inputsnippets{GaiaToHydra/T1BridgeUse}

@@

 \inputsnippets{GaiaToHydra/LocateT1, GaiaToHydra/T1BridgeUseb}
